On change of priors in one-vs-one classification methods

### 2025-05-08 coupling.tex
Fix Table1

\begin{prop}
Suppose the coupling methods $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are Bayes covariant. If $\sum a_m = 1$, then $\boldsymbol{e} = \bigoplus_m a_m \boldsymbol{v}_m$ is also a Bayes covariant coupling method.
\end{prop}

@@

\begin{proof}
Let 
\begin{align}
	\boldsymbol{R}_s \stackrel{def}{=} \begin{pmatrix} \cdot & s & 1 -s \\  1-s & \cdot & s \\ s & 1-s & \cdot \end{pmatrix}
\end{align}
Since $R_s$ is invariant under the action of any permutation of 3 elements, 
for a symmetric coupling method we have 
\begin{align}
	\boldsymbol{v} (\boldsymbol{R}_s) = \biggl(\frac 13, \frac 13, \frac 13 \biggr).
\end{align}
Now applying  Proposition \ref{prop:bc3} from Appendix \ref{app:bc1} yields uniqueness. The existence of the method was already shown above.
\end{proof}

Let us point out one consequence of the theorem. We could define another ensemble $\tilde{\boldsymbol{e}}$ by averaging the predictions of $\boldsymbol{s}_1, \boldsymbol{s}_2, \boldsymbol{s}_3$:
\[
\tilde{\boldsymbol{e}} = \frac13 \boldsymbol{s}_1(x) + \frac13 \boldsymbol{s}_2(x) + \frac 13 \boldsymbol{s}_3(x).
\]
Note that here we use the plus symbol to denote the vector addition of vectors representing $K$-class probability distributions. This is a different classifier from the one given by  \eqref{eq:bc1} (see Appendix \ref{app:explicit}), and since it is symmetric, it cannot be Bayes covariant.

@@

The following table indicates which properties are enjoyed by each coupling method we described in this section.

\begin{table}[!ht]
\begin{tabular}{cm{2.5cm}m{1.5cm}m{1.5cm}ccm{1.5cm}m{1.5cm}}
&property & Hastie-Tibshirani & Wu-Lin-Weng & radial & normal & arboreal & Hinton's oracle \\
\hline 
\multirow{5}{*}{\begin{turn}{90}\makecell{exact}\end{turn}}
&uniqueness &  yes & yes & yes & yes & yes & yes \\
&Bradley-Terry consistency & yes & yes & yes & yes & yes & yes \\
&canonicity & yes & no & yes & yes & no & yes \\
&symmetry & yes & yes & yes & yes & no & yes \\
& Bayes covariant & no & no & no & yes & yes & yes \\
\hline
\multirow{5}{*}{\begin{turn}{90}\makecell{non-exact}\end{turn}}
&Hinton's minimality & ? & ?  & ++ & ?  & ? & +++ \\
&lack of parameters & yes & yes & yes & yes & yes & yes \\
& amounts to a linear system & no & yes & yes & yes & yes & yes\\
& linear system of special form & no & no & yes & yes & yes & yes \\
& iterative method & yes & yes & yes & no & not needed & not needed\\
\hline
\end{tabular}
\caption{Summary of properties of coupling methods described in Section \ref{sec:coupling}.}
\label{tab:summaryCoupling}
\end{table}

>>>>

\begin{prop}
	\label{prop:ensemble}
Suppose the coupling methods $\boldsymbol{v}_1, \ldots, \boldsymbol{v}_M$ are Bayes covariant. If $\sum a_m = 1$, then $\boldsymbol{e} = \bigoplus_m a_m \boldsymbol{v}_m$ is also a Bayes covariant coupling method.
\end{prop}

@@

\begin{proof}
Let 
\begin{align}
	\boldsymbol{R}_s \stackrel{def}{=} \begin{pmatrix} \cdot & s & 1 -s \\  1-s & \cdot & s \\ s & 1-s & \cdot \end{pmatrix}
\end{align}
Since $R_s$ is invariant under the action of any permutation of 3 elements, 
for a symmetric coupling method we have 
\begin{align}
	\boldsymbol{v} (\boldsymbol{R}_s) = \biggl(\frac 13, \frac 13, \frac 13 \biggr).
\end{align}
Now applying  Proposition \ref{prop:bc3} from Appendix \ref{app:bc1} yields uniqueness. The existence of the method was already shown above using Proposition \ref{prop:ensemble}.
\end{proof}

Let us point out one consequence of the theorem. We could define another ensemble $\tilde{\boldsymbol{e}}$ by averaging the predictions of $\boldsymbol{s}_1, \boldsymbol{s}_2, \boldsymbol{s}_3$:
\[
\tilde{\boldsymbol{e}} = \frac13 \boldsymbol{s}_1(x) + \frac13 \boldsymbol{s}_2(x) + \frac 13 \boldsymbol{s}_3(x).
\]
Note that here we use the plus symbol to denote the vector addition of vectors representing  probability distributions over $K$ classes. This is a different classifier from the one given by  \eqref{eq:bc1} (see Appendix \ref{app:explicit}), and since it is symmetric, it cannot be Bayes covariant.

@@

In this section  we summarize properties of coupling methods described earlier in this section.  Table \ref{tab:summaryCoupling} concisely lists the relevant properties enjoyed by each method. Note that we have split the desideratum ``simplicity of computation'' into three different aspects:
\begin{itemize}
	\item whether a coupling method amounts to a linear system of equations,
	\item if the coupling method amounts to a linear system of equations, whether the equations are of a special form (e.g. a Markov matrix) that facilitates their solution,
	\item whether the authors who published the method provide an iterative method that implements the estimate. Iterative methods are often  faster than Gaussian elimination, and less prone to numerical issues.
\end{itemize}

 %interpretation of exact desiderate is unambiguous.

%The following table indicates which properties are enjoyed by each coupling method we described in this section.

\begin{table}[!ht]
\begin{tabular}{cm{2.5cm}m{1.5cm}m{1.5cm}ccm{1.5cm}m{1.5cm}}
&property & Hastie-Tibshirani & Wu-Lin-Weng & radial & normal & arboreal & Hinton's oracle \\
\hline 
\multirow{5}{*}{\begin{turn}{90}\makecell{exact}\end{turn}}
&uniqueness &  yes & yes & yes & yes & yes & yes \\
&Bradley-Terry consistency & yes & yes & yes & yes & yes & yes \\
&canonicity & yes & no & yes & yes & no & yes \\
&symmetry & yes & yes & yes & yes & no & yes \\
& Bayes covariant & no & no & no & yes & yes & yes \\
\hline
\multirow{5}{*}{\begin{turn}{90}\makecell{non-exact}\end{turn}}
&Hinton's minimality & N/A & \multicolumn{5}{c}{see Section \ref{sec:exp1}} \\
&robustness & N/A & \multicolumn{5}{c}{see Section \ref{sec:exp1}} \\
&lack of parameters & yes & yes & yes & yes & yes & yes \\
& amounts to a linear system & no & yes & yes & yes & yes & yes\\
& linear system of special form & N/A & no & yes & yes & yes & yes \\
& iterative method & yes & yes & yes & no & not needed & not needed\\
\hline
\end{tabular}
\caption{Summary of properties of coupling methods described in Section \ref{sec:coupling}.}
\label{tab:summaryCoupling}
\end{table}
